---
title: "Multi-cancer correlation-survival analysis"
author: "Siwakorn"
date: "2021/3/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Library
```{r}
library(tidyverse)
library(RTCGA.clinical)
library(survminer)
library(survival)
library("cluster")
library("magrittr")
library("biomaRt")
library(corrplot)
library(reshape2)
```

#Setting up
```{r}
name <- c("LUSC","LUAD","BRCA","COAD","OV","BLCA","HNSC","LIHC","READ","STAD")
Count.Dir <- c("/yshare1/home/siwakorn/TCGA/DataPortal/GDC.TCGA.LUSC/TCGA-LUSC.htseq_fpkm.tsv",
              "/yshare1/home/siwakorn/TCGA/DataPortal/GDC.TCGA.LUAD/TCGA-LUAD.htseq_fpkm.tsv",
              "/yshare1/home/siwakorn/TCGA/DataPortal/GDC.TCGA.BRCA/TCGA-BRCA.htseq_fpkm.tsv",
              "/yshare1/home/siwakorn/TCGA/DataPortal/GDC.TCGA.COAD/TCGA-COAD.htseq_fpkm.tsv",
              "/yshare1/home/siwakorn/TCGA/DataPortal/GDC.TCGA.OVCA/TCGA-OV.htseq_fpkm.tsv",
              "/yshare1/home/siwakorn/TCGA/DataPortal/GDC.TCGA.BLCA/TCGA-BLCA.htseq_fpkm.tsv",
              "/yshare1/home/siwakorn/TCGA/DataPortal/GDC.TCGA.HNSC/TCGA-HNSC.htseq_fpkm.tsv",
              "/yshare1/home/siwakorn/TCGA/DataPortal/GDC.TCGA.LIHC/TCGA-LIHC.htseq_fpkm.tsv",
              "/yshare1/home/siwakorn/TCGA/DataPortal/GDC.TCGA.READ/TCGA-READ.htseq_fpkm.tsv",
              "/yshare1/home/siwakorn/TCGA/DataPortal/GDC.TCGA.STAD/TCGA-STAD.htseq_fpkm.tsv"
              
              )
Surv.Dir <- c("/home/siwakorn/TCGA/DataPortal/GDC.TCGA.LUSC/TCGA-LUSC.survival.tsv",
              "/home/siwakorn/TCGA/DataPortal/GDC.TCGA.LUAD/TCGA-LUAD.survival.tsv",
              "/home/siwakorn/TCGA/DataPortal/GDC.TCGA.BRCA/TCGA-BRCA.survival.tsv",
              "/home/siwakorn/TCGA/DataPortal/GDC.TCGA.COAD/TCGA-COAD.survival.tsv",
              "/home/siwakorn/TCGA/DataPortal/GDC.TCGA.OVCA/TCGA-OV.survival.tsv",
              "/home/siwakorn/TCGA/DataPortal/GDC.TCGA.BLCA/TCGA-BLCA.survival.tsv",
              "/home/siwakorn/TCGA/DataPortal/GDC.TCGA.HNSC/TCGA-HNSC.survival.tsv",
              "/home/siwakorn/TCGA/DataPortal/GDC.TCGA.LIHC/TCGA-LIHC.survival.tsv",
              "/home/siwakorn/TCGA/DataPortal/GDC.TCGA.READ/TCGA-READ.survival.tsv",
              "/home/siwakorn/TCGA/DataPortal/GDC.TCGA.STAD/TCGA-STAD.survival.tsv"
              )
Count <- list()
Count.mod <- list()
Surv <- list()
ensembl <- useMart("ensembl")
Human.ensembl = useDataset("hsapiens_gene_ensembl",mart=ensembl)
```

#Data Preparation - Expression matrix (Count)
```{r}
for(i in 1:10){
      print(name[i])
      Count[[i]] <- read.table(file = Count.Dir[i], sep = "\t", header= T)
      print(Count[[i]][1:10,1:10])
      Count.mod[[i]] <- Count[[i]][,-1] %>% t() %>% as.data.frame()
      colnames(Count.mod[[i]]) <- Count[[i]]$Ensembl_ID
      print(Count.mod[[i]][1:10,1:10])
      GenePool = colnames(Count.mod[[i]])
      tmp = data.frame("Original" = GenePool,
                       "New" = unlist(lapply(GenePool, function(x) substr(x,1,15) ))
                       )
      tmp2 = getBM(attributes =c("ensembl_gene_id", "ensembl_gene_id_version", "external_gene_name"), 
                   filters = "ensembl_gene_id",
                   values = tmp$New ,
                   mart = Human.ensembl,
                   useCache = FALSE
                   )
      tmp2$New <- tmp2$ensembl_gene_id
      tmp3 = left_join(tmp,tmp2)
      tmp3[is.na(tmp3$ensembl_gene_id),]$external_gene_name <- as.character(tmp3[is.na(tmp3$ensembl_gene_id),]$Original )
      print(summary(tmp3$Original == colnames(Count.mod[[i]]))  )   #Validation
      colnames(Count.mod[[i]]) <- tmp3$external_gene_name           #Add Label
      Count.mod[[i]] <- Count.mod[[i]][,!colSums(Count.mod[[i]]) == 0]                      #Remove Gene (column) with 0 sum
      print(Count.mod[[i]][1:10,1:10])
}
names(Count.mod) <- name
lapply(Count.mod, dim)
#saveRDS(Count.mod,file = "/yshare1/home/siwakorn/TCGA/RDS/GDC.10MultiCancer.ExpressionMatrix.210322.rds" )
Count.mod = readRDS(file = "/home/siwakorn/TCGA/RDS/GDC.10MultiCancer.ExpressionMatrix.210322.rds" )
```

#Data Preparation - Survival
```{r}
selected.genes <- c("PTGS1","PTGS2","PTGER2","PTGER4")
Surv.mod <- list()
for(i in 1:10){
      print(name[i])
      Surv[[i]] <- read.table(file = Surv.Dir[i], sep = "\t", header= T)
      Surv[[i]]$sample.new <- gsub("-",".",Surv[[i]]$sample)                                                             #Convert sample name
      print(nrow(Count.mod[[i]]))
      print(intersect(rownames(Count.mod[[i]]), Surv[[i]]$sample.new) %>% length())
      tmp1 = dplyr::select(Surv[[i]], sample.new, OS, OS.time)
      colnames(tmp1)[1] <- "Sample"
      tmp2 = dplyr::select(Count.mod[[i]], PTGS1,PTGS2,PTGER2,PTGER4) %>% as_tibble(rownames = "Sample")
      data1  <- left_join(tmp1,tmp2)
      data = na.omit(data1)
      for(j in selected.genes ){
            L = rep(paste0(j,".Intermediate"),nrow(data))
            E = data[,j]
            L[E < quantile(E, c(0.33,0.66))[1]] <- paste0(j,".Low") 
            L[E > quantile(E, c(0.33,0.66))[2]] <- paste0(j,".High") 
            data[,paste0(j,".Group")] <- L
      }
      #Combine 2 genes
      GeneSet = list(c("PTGS1","PTGS2"), c("PTGER2","PTGER4"))
      SetName =c("COX","EP2_EP4")
      for(k in 1:2){
            a= GeneSet[[k]][1]
            b= GeneSet[[k]][2]
            tmp <- paste0(data[,paste0(a,".Group")],"-",data[,paste0(b,".Group")])
            tmp[-c(grep(paste0(a,".High-",b,".High"), tmp ),grep(paste0(a,".Low-",b,".Low"), tmp ))] <- paste0(SetName[k], "-Intermediate")
            tmp[c(grep(paste0(a,".High-",b,".High"), tmp ))] <- paste0(SetName[k], "-High")
            tmp[c(grep(paste0(a,".Low-",b,".Low"), tmp ))] <- paste0(SetName[k], "-Low")
            data[,paste0(a,"_",b)] <- factor(tmp, levels = c( paste0(SetName[k], "-High"), 
                                                              paste0(SetName[k], "-Intermediate") ,
                                                              paste0(SetName[k], "-Low") 
                                                              ) 
                                             )
            q1a = quantile(data[,a], c(0.33,0.66) )[1]
            q4a = quantile(data[,a], c(0.33,0.66) )[2]
            q1b = quantile(data[,b], c(0.33,0.66) )[1]
            q4b = quantile(data[,b], c(0.33,0.66) )[2]
            #png(filename = paste0("/yshare1/home/siwakorn/TCGA/Fig/GDC.TCGA.ExpressionProfile.",name[i],".",SetName[k],".png"), width =800, height = 800)
            print(
                  ggplot(data, aes_string(x = a, y = b, color = paste0(a,"_",b))) + 
                  ggtitle(paste0(name[i], " ", SetName[k])) +      
                  geom_point() + 
                  geom_hline(yintercept = q1b) + geom_hline(yintercept = q4b)+
                  geom_vline(xintercept = q1a) + geom_vline(xintercept = q4a)+
                  theme_classic() +
                  theme(axis.title = element_text(size = 27))
                  )
            #dev.off()
            Surv.mod[[name[i] ]] <- data
            print(Surv.mod[[name[i] ]] )
      }
}
lapply(Surv.mod, dim)
#saveRDS(Surv.mod,file = "/yshare1/home/siwakorn/TCGA/RDS/GDC.10MultiCancer.Survival.210322.rds" )
#Surv.mod <- readRDS(file = "/home/siwakorn/TCGA/RDS/GDC.10MultiCancer.Survival.210322.rds" )

#Surv.mod.bk <- Surv.mod
```


#COX score
```{r}
for(i in 1:10){
      Surv.mod[[i]]$COX_Score1 <- (Surv.mod[[i]]$PTGS1 + Surv.mod[[i]]$PTGS2)/2
      Surv.mod[[i]]$COX_Score2 <- (Surv.mod[[i]]$PTGER2 + Surv.mod[[i]]$PTGER4)/2
      Surv.mod[[i]]$COX_Score3 <- (Surv.mod[[i]]$PTGS1 + Surv.mod[[i]]$PTGS2 + Surv.mod[[i]]$PTGER2 + Surv.mod[[i]]$PTGER4)/4
      for(j in 1:2){
            tmp = paste0("COX_Score",j)
            a = quantile(Surv.mod[[i]][,tmp], c(0.33,0.66))[1]
            b = quantile(Surv.mod[[i]][,tmp], c(0.33,0.66))[2]
            label <- rep("COX-Intermediate",nrow(Surv.mod[[i]]) )
            label[Surv.mod[[i]][,tmp] < a ] <- "COX-Low"
            label[Surv.mod[[i]][,tmp] > b ] <- "COX-High"
            Surv.mod[[i]][,paste0(tmp,".Group")] <- label
            Surv.mod[[i]][,paste0(tmp,".Group")] <- factor(Surv.mod[[i]][,paste0(tmp,".Group")], levels = paste0("COX-", c("High","Intermediate","Low")))
      }
}
```

#PTGER score
```{r}
cutoff <- list(c(0.2,0.8), c(0.25,0.75), c(0.33,0.66))
cutoff[[1]]
for(i in 1:10){
      Surv.mod[[i]]$PTGER_Score <- (Surv.mod[[i]]$PTGER2 + Surv.mod[[i]]$PTGER4)/2
      #Surv.mod[[i]]$COX_Score3 <- (Surv.mod[[i]]$PTGS1 + Surv.mod[[i]]$PTGS2 + Surv.mod[[i]]$PTGER2 + Surv.mod[[i]]$PTGER4)/4
      for(j in 1:3){
            tmp = "PTGER_Score"
            a = quantile(Surv.mod[[i]][,tmp], cutoff[[j]]  )[1]
            b = quantile(Surv.mod[[i]][,tmp], cutoff[[j]]  )[2]
            label <- rep("PTGER-Intermediate",nrow(Surv.mod[[i]]) )
            label[Surv.mod[[i]][,tmp] < a ] <- "PTGER-Low"
            label[Surv.mod[[i]][,tmp] > b ] <- "PTGER-High"
            Surv.mod[[i]][,paste0(tmp,".Group",j)] <- label
            Surv.mod[[i]][,paste0(tmp,".Group",j)] <- factor(Surv.mod[[i]][,paste0(tmp,".Group",j)], levels = paste0("PTGER-", c("High","Intermediate","Low")))
      }
}


Surv.mod[[1]]
for(i in 1:10){
      for(j in 1:3){
            print(
                  ggplot(Surv.mod[[i]], aes_string(x = "PTGER2", y ="PTGER4", color = paste0("PTGER_Score.Group",j) ) ) +
                        geom_point()
            )
      }
      
}
```


#Plot Survival x PTGER score
```{r,fig.width=5,fig.height=5}
tmp = c(".Q20-80",".Q25-75",".Q33-66")
for(j in 1:10){
      for(i in 1:2){
            Surv.mod[[j]]$Group <-  Surv.mod[[j]][,paste0("PTGER_Score.Group",i)]
            Surv.mod2[[j]] <- filter(Surv.mod[[j]], !Group == "PTGER-Intermediate")               #Remove COX intermediate
            fit <-  survfit(Surv(OS.time,OS ) ~ Group, data = Surv.mod2[[j]]   ) 
            plot = ggsurvplot(fit, data = Surv.mod2[[j]], 
                              risk.table = F,
                              size =2,
                              pval = T,
                              palette = c("red", "black","dodgerblue"),
                              xlim = c(0,1826),
                              break.time.by = 200,
                              cumevents = F,
                              cumcensor = F
                              ) +
                   ggtitle(paste0("SURVIVORSHIP OF ", name[j], " x PTGER-score ",i )) 
            #tiff(filename = paste0("/yshare1/home/siwakorn/TCGA/Fig.Revision/GDC.TCGA.Fig6F.Survival.",name[j],".PTGERSCORE",i,tmp[i],".tiff"), width =8, height =8, units = "in", res = 300  )
           # png(filename = paste0("/yshare1/home/siwakorn/TCGA/Fig/GDC.10Cancers/GDC.TCGA.Survival.",name[j],".PTGERSCORE",i,tmp[i],".png"), width =800, height = 800)
            print(plot)
            #dev.off()
      }      
}
fit %>% str()
fit$
```






#Correlation
##Correlation heatmap (Single cancer)
```{r}
selected.genes = c("TNFSF4","TNFRSF4","FOXP3","TNFRSF9","CCL17","CCL22","PTGS1","PTGER2","PTGER4","PTGS2","IL6","CXCL2","FOS","NR4A1","VEGFD","CXCL8") 

for(j in 1:10){
      df.mod <- Count.mod[[j]]
      df.cor <- dplyr::select(df.mod, selected.genes) %>% cor() %>% round(2)
      melted_cormat <- melt(df.cor)
      for(i in 1){
            tiff(filename = paste0("/yshare1/home/siwakorn/TCGA/Fig.Revision/GDC.TCGA.Correlation.",name[j],".210406.tiff" ),
                width = 12, 
                height = 12,
                units = "in",
                res = 300)
            print(
                  ggplot(melted_cormat, aes(Var2, Var1, fill = value))+
                  geom_tile(color = "white")+
                  geom_text(aes(Var2,Var1,label = value), color ="black",size=5) +
                  scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1), 
                                       space = "Lab",name="Pearson\nCorrelation",na.value = "white")  +
                  theme_minimal()+ # minimal theme
                  theme(axis.text.x = element_text(angle = 90, vjust = 1, color ="black",  size = 20, hjust = 1),
                        axis.text.y = element_text(color = "black", size = 20 ),
                        axis.title = element_blank())+
                  coord_fixed()
      )
      dev.off()

}
}
df.cor
df.mod
```

```{r}
j=1
df.mod <- Count.mod[[j]]
df.cor <- dplyr::select(df.mod, selected.genes)  %>% cor() %>% round(2)
df.cor
```


```{r}
df.cor
```

##Heatmap of MultiCancer x SelectedGene
```{r}

selected.genes = c("PTGER2","PTGER4","PTGS1","CCL17","CCL22","FOXP3","CTLA4","IL2RA","TNFRSF9","PTGS2","IL6","CXCL2","CXCL8","IL1B","VEGFA","VEGFD","OSM")
selected.group = "PTGER_Score.Group2"
df.heatmap <- data.frame()
for(i in 1:10){
      df <- Count.mod[[i]][,selected.genes] %>% as_tibble(rownames = "Sample")
      Surv.mod[[i]]$Group <- Surv.mod[[i]][,selected.group] 
      tmp = Surv.mod[[i]] %>% as_tibble() %>% dplyr::select(Sample,Group)           
      df <- left_join(tmp, df, by = "Sample") %>% na.omit()
      df
      df.mean <- as.data.frame(matrix(nrow =0, ncol = (length(selected.genes))))
      colnames(df.mean) <- c(selected.genes)
      m=1
      df$Group <- as.factor(df$Group)
      for(j in levels(df$Group)){
            df2 <- filter(df, Group == j) %>% dplyr::select(selected.genes)
            df2
            df.mean[m,] <- c(as.vector(colMeans(df2) ))
            m=m+1
      }
      df.scale <- as.data.frame(apply(df.mean, 2, scale) )
      df.scale$Group <- levels(df$Group)
      df.scale$Cancer <- name[i]
      df.heatmap <- rbind(df.heatmap, df.scale)
}

df.heatmap <- df.heatmap %>% gather("Gene","Expression", -Cancer, -Group,) %>% dplyr::select(Cancer,Group,Gene,Expression)
df.heatmap$Expression <- as.numeric(df.heatmap$Expression)
df.heatmap$Gene <- factor(df.heatmap$Gene, levels = selected.genes)
df.heatmap$Group <- factor(df.heatmap$Group, levels = levels(df$Group))
df.heatmap$Cancer <- gsub("OVCA","OV",df.heatmap$Cancer)
df.heatmap$Cancer <- factor(df.heatmap$Cancer, levels = name )
df.heatmap2 <- filter(df.heatmap, !Gene %in% c("TGFB1","MMP9","TNF"))# %>% filter(Cancer %in% c("LUSC","BRCA","OV","LIHC") )
df.heatmap2 <- filter(df.heatmap2, Cancer %in% c("BRCA","LUSC","OV","LIHC") )
df.heatmap %>% filter(Gene == "PTGER4")
df.heatmap2 
for(i in 1){
      #png(filename = "/yshare1/home/siwakorn/TCGA/Fig/GDC.10Cancers/GDC.TCGA.10Cancer.Heatmap.PTGERScore2.2.png", width = 1000, height = 500)
      #tiff(filename = "/yshare1/home/siwakorn/TCGA/Fig.Revision/GDC.TCGA.10Cancer.Heatmap.PTGERScore2.tiff", width = 15, height = 15, units = "in", res = 300)
      tiff(filename = "/yshare1/home/siwakorn/TCGA/Fig.Revision/GDC.TCGA.10Cancer.Fig6E.Heatmap.PTGERScore2.V2.tiff", width = 9, height = 7.5, units = "in", res = 500)
      print(
            ggplot(df.heatmap2, aes(y = Group, x = Gene, fill = Expression)) + 
                  geom_tile(color = "white") +
                  facet_grid(Cancer ~ . ) +                
                  scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", 
                  space = "Lab",name="Scale Expression" ,na.value = "white")  +
                  ylab("Cancer") +
                  theme(axis.text.x = element_text(angle = 90,color = "black",size= 20, hjust=1 ),
                        axis.text.y = element_text(color="black",size= 20, hjust =0),
                        text= element_text(color ="black"),
                        strip.background.y = element_rect(fill="black"),
                        legend.position = "bottom",
                        strip.text.y = element_text(face = "bold", hjust=0.5, color="white",size= 23)
                        )
      )
      dev.off()
}
df2 <- gather("Gene","Expression")
ggplot(df, aes(x = Group, y = TNFSF4) ) + geom_jitter()

Surv.mod[[1]]
Count.mod[["LUSC"]][1:10,selected.genes]

lapply(Surv.mod, dim)
```

##ScatterPlot for correlation
```{r}
library(ggpubr)
df.mod <- Count.mod[[1]]
selected.genes <- c("CCL17","CCL22","FOXP3","TNFRSF9")
for(i in selected.genes){
      tiff(filename = paste0("/yshare1/home/siwakorn/TCGA/Fig.Revision/GDC.LUSC.FigS7.Scatter.V2.PTGS1-",i,".tiff") , width = 8, height = 8, units = "in", res = 300)
      #png(filename = folder("Fig",paste0("GDC.LUSC.Scatter.PTGS1-",i,".png") ), width = 800, height = 800)
      print(
            ggscatter(df.mod, x = "PTGS1", y = i, 
                      add = "reg.line", conf.int = TRUE, 
                      cor.coef = TRUE, cor.method = "pearson")+
                  theme(axis.title = element_text(size =27))
      )
      dev.off()
}
selected.genes = c("IL6","CXCL2","VEGFD","OSM")
for(i in selected.genes){
      tiff(filename = paste0("/yshare1/home/siwakorn/TCGA/Fig.Revision/GDC.LUSC.FigS7.Scatter.V2.PTGS2-",i,".tiff") , width = 8, height = 8, units = "in", res = 300)
      #png(filename = folder("Fig",paste0("GDC.LUSC.Scatter.PTGS2-",i,".png") ), width = 800, height = 800)
      print(
            ggscatter(df.mod, x = "PTGS2", y = i, 
                      add = "reg.line", conf.int = TRUE, 
                      cor.coef = TRUE, cor.method = "pearson")+
                  theme(axis.title = element_text(size =27))
      )
      dev.off()
}
```



#Genomewide correlation (RScript)
```{r}
x = 3
df.mod <- readRDS(file = "/yshare1/home/siwakorn/TCGA/RDS/GDC.MultiCancer.ExpressionMatrix.210321.rds" )
df.mod <- df.mod[[x]]
selected.genes <- colnames(df.mod)
table = as.data.frame(matrix(ncol = 9, nrow = 0) )
colnames(table) = c("Gene1","Gene2","p_val","t","df","correlation","Method","95%CI.1","95%CI.2")
Stat<-list()
m=1
for(k in c("PTGS1","PTGS2","PTGER2","PTGER4")){
      for(i in selected.genes){
            test <- cor.test(df.mod[,k],df.mod[,i] )
            table[m,] <- c(k,i,test$p.value,test$statistic, test$parameter,test$estimate, test$method,test$conf.int)
            m=m+1
            if( length(intersect(m, seq(1000,2000000,5000))) != 0 ) {
                  print(paste0(m, " ", i))
            }
      }
	Stat[[k]] <- table
	table = as.data.frame(matrix(ncol = 9, nrow = 0) )
	colnames(table) = c("Gene1","Gene2","p_val","t","df","correlation","Method","95%CI.1","95%CI.2")
	m=1
}
#saveRDS(Stat, file = paste0("/yshare1/home/siwakorn/TCGA/RDS/GDC.BRCA.StatisticList.Final.210321.rds"))
Stat <- readRDS(file = paste0("/yshare1/home/siwakorn/TCGA/RDS/GDC.BRCA.StatisticList.Final.210321.rds"))
```


#Deprecated code


##How to modify Survial plot
```{r}
plot[[1]] + 
      theme(axis.title.x = element_text(size =20, 
                                        face = "bold", 
                                        color ="blue"),
            plot.title = element_text(face = "bold")
            )
plot[[1]] +
      guides(colour = guide_legend("Group", title.theme = element_text(size =20),
                                   label.theme = element_text(colour = "pink"))
             )
ggsurvplot(fit, 
           data = Surv.mod2[[j]], 
           risk.table = F,
           size =2,
           pval = T,
           pval.size =5,
           palette = c("red", "black","dodgerblue"), 
           xlim = c(0,1826), break.time.by = 200,cumevents = F, cumcensor = F) 
```





##Function customize label
```{r}
customize_labels <- function (p, font.title = NULL,
                              font.subtitle = NULL, font.caption = NULL,
                              font.x = NULL, font.y = NULL, font.xtickslab = NULL, font.ytickslab = NULL)
{
  original.p <- p
  if(is.ggplot(original.p)) list.plots <- list(original.p)
  else if(is.list(original.p)) list.plots <- original.p
  else stop("Can't handle an object of class ", class (original.p))
  .set_font <- function(font){
    font <- ggpubr:::.parse_font(font)
    ggtext::element_markdown (size = font$size, face = font$face, colour = font$color)
  }
  for(i in 1:length(list.plots)){
    p <- list.plots[[i]]
    if(is.ggplot(p)){
      if (!is.null(font.title)) p <- p + theme(plot.title = .set_font(font.title))
      if (!is.null(font.subtitle)) p <- p + theme(plot.subtitle = .set_font(font.subtitle))
      if (!is.null(font.caption)) p <- p + theme(plot.caption = .set_font(font.caption))
      if (!is.null(font.x)) p <- p + theme(axis.title.x = .set_font(font.x))
      if (!is.null(font.y)) p <- p + theme(axis.title.y = .set_font(font.y))
      if (!is.null(font.xtickslab)) p <- p + theme(axis.text.x = .set_font(font.xtickslab))
      if (!is.null(font.ytickslab)) p <- p + theme(axis.text.y = .set_font(font.ytickslab))
      list.plots[[i]] <- p
    }
  }
  if(is.ggplot(original.p)) list.plots[[1]]
  else list.plots
}
```

##Survival ------------------
##Plot
```{r}
selected.genes <- c("PTGS1","PTGS2","PTGER2","PTGER4")
for(j in 1:10){
      for(i in selected.genes ){
            Surv.mod[[j]]$Group <-  Surv.mod[[j]][,paste0(i,".Group")]
            fit <-  survfit(Surv(OS.time,OS ) ~ Group, data = Surv.mod[[j]]   ) 
            png(filename = paste0("/yshare1/home/siwakorn/TCGA/Fig/GDC.10Cancers/GDC.TCGA.Survival.",name[j],".",i,".210323.png" ),
                width = 800, 
                height = 800)
            plot = ggsurvplot(fit, data = Surv.mod[[j]], 
                              risk.table = F,
                              pval = T,
                              size =2,
                              palette = c("red", "black","dodgerblue"),
                              xlim = c(0,3650),
                              break.time.by = 200
                              ) + 
            ggtitle(paste0("SURVIVORSHIP OF ", name[j], " x ",i )) 
            plot <- customize_labels(plot,
                              font.y        = c(27, "bold", "black"),
                              font.x        = c(27, "bold", "black")
                              )
      print(plot)
      dev.off()
      }
}


```

##Plot Combine COX1 COX2
```{r}
Surv.mod2 <- list()
levels(Surv.mod[[1]]$PTGS1_PTGS2)
for(i in 1:5){
      Surv.mod2[[i]] <- filter(Surv.mod[[i]], PTGS1_PTGS2 %in% c("COX-High","COX-Low") )
      fit <-  survfit(Surv(OS.time,OS ) ~ PTGS1_PTGS2, data = Surv.mod2[[i]]   )
      plot = ggsurvplot(fit, data = Surv.mod2[[i]], 
                 risk.table = F,
                 size =2,
                 palette = c("red", "dodgerblue"),
                 pval =T,
                 pval.method = T,
                 #legend.labs = c("COX1 High COX2 High", "Other", "COX1 Low CO2 Low"),          #For 3 groups
                 #palette = c("red", "black","dodgerblue"),                                     #For 3 groups
                 xlim = c(0,1826),
                 break.time.by = 200
                 ) + 
      
            ggtitle(paste0("SURVIVORSHIP OF ", name[i])) 
      plot <- customize_labels(plot,
                               font.y        = c(27, "bold", "black"),
                               font.x        = c(27, "bold", "black")
                               )
      png(filename = paste0("/yshare1/home/siwakorn/TCGA/Fig/GDC.TCGA.Survival.",name[i],".COX.210322.png" ), width = 1200, height = 800)
      print(
            plot
            ) 
      dev.off()
}
Surv.mod[[1]]
``` 

##Plot Combine EP2 EP4
```{r}
for(i in 1:5){
      fit <-  survfit(Surv(OS.time,OS ) ~ PTGER2_PTGER4, data = Surv.mod[[i]]   )
      plot = ggsurvplot(fit, data = Surv.mod[[i]], 
                 risk.table = F,
                 size =2,
                 legend.labs = c("PTGER2 High PTGER4 High", "Other", "PTGER2 Low PTGER4 Low"),
                 palette = c("red", "black","dodgerblue"),
                 #xlim = c(0,1826),
                 #break.time.by = 200
                 ) + 
      
            ggtitle(paste0("SURVIVORSHIP OF ", name[i], " x ", "PTGER2-PTGER4")) 
      plot <- customize_labels(plot,
                               font.y        = c(27, "bold", "black"),
                               font.x        = c(27, "bold", "black")
                               )
      png(filename = paste0("/yshare1/home/siwakorn/TCGA/Fig/GDC.MultiCancer/GDC.TCGA.Survival.",name[i],".EP2-EP4.210321.png" ), width = 1200, height = 800)
      print(
            plot
            ) 
      dev.off()
}
```


##Plot COX socre
```{r}
for(j in 1:10){
      Surv.mod2[[j]] <- Surv.mod[[j]] 
      for(i in 2){
            Surv.mod2[[j]]$Group <-  Surv.mod2[[j]][,paste0("COX_Score",i,".Group")]
            Surv.mod2[[j]] <- filter(Surv.mod2[[j]], !Group == "COX-Intermediate")               #Remove COX intermediate
            Surv.mod2[[j]]
            fit <-  survfit(Surv(OS.time,OS ) ~ Group, data = Surv.mod2[[j]]   ) 
            plot = ggsurvplot(fit, data = Surv.mod2[[j]], 
                              risk.table = F,
                              size =2,
                              pval = T,
                              palette = c("red", "black","dodgerblue"),
                              xlim = c(0,1826),
                              break.time.by = 200,
                              cumevents = F,
                              cumcensor = F
                              ) +
                   ggtitle(paste0("SURVIVORSHIP OF ", name[j], " x COX-score ",i )) 
            #png(filename = paste0("/yshare1/home/siwakorn/TCGA/Fig/GDC.10Cancers/GDC.TCGA.Survival.3Q3366.",name[j],".COXSCORE",i,".png"), width =800, height = 800)
            print(plot)
            dev.off()
      }      
}
```



